\RequirePackage{xifthen}

\documentclass[11pt,a4paper,sans]{awesomecv}

%%\moderncvtheme[blue]{classic}

\usepackage{fontspec}

\newfontfamily\cambria[
  Path=fonts/,
  UprightFont=*-Regular,
  ItalicFont=*-Italic,
  BoldFont=*-Bold,
  BoldItalicFont=*-BoldItalic,
]{Cambria}

%\renewcommand*{\sectionstyle}[1]{{\fontsize{16pt}{1em}\cambria\bfseries\color{text}\@sectioncolor #1}}

\usepackage[utf8]{inputenc}

\usepackage[unicode]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

\usepackage{enumitem}

\name{Aleksei}{Savelev}
\position{Software Developer}
\mobile{+7~911~250~4587}
\mobile{+62~821~4523~4068}
\email{savelichalex93@gmail.com}
\github{savelichalex}

\begin{document}
\makecvheader[C]

\let\bodyfont\cambria

\newcommand{\cvlistitem}[1]{\item {\fontsize{12pt}{1em}\bodyfont\upshape\color{darktext} #1}}
\newenvironment{cvlist}{
  \begin{description}[
      itemindent=0em,
      labelwidth=0em,
      labelsep=0em,
      leftmargin=0em,
      parsep=1ex
    ]
}{
  \end{description}
}

\newcommand{\cvdescriptionitem}[2]{\item[{\fontsize{12pt}{1em}\bodyfont\bfseries\color{darktext} #1}] {\fontsize{12pt}{1em}\cambria\upshape\color{darktext} #2}}
\newenvironment{cvdescription}{
  \begin{description}[
      parsep=1ex,
    ]
}{
  \end{description}
}

\cvsection{Key areas of expertise}
\begin{cvlist}
  \cvlistitem{Web frontend development}
  \cvlistitem{Cross-platform mobile applications (ReactNative)}
\end{cvlist}

\cvsection{Technical Skills}
\begin{cvdescription}
\cvdescriptionitem{Languages}{TypeScript, JavaScript, Objective-C, Java}
\cvdescriptionitem{VCS}{Git}
\cvdescriptionitem{OS}{macOS, iOS, Android}
\cvdescriptionitem{Development tools}{VS Code, Xcode, Android Studio, Emacs}
\end{cvdescription}

\renewcommand*{\entrypositionstyle}[1]{{\fontsize{12pt}{1em}\bodyfont\bfseries\color{darktext} #1}}
\renewcommand*{\entrydatestyle}[1]{{\fontsize{11pt}{1em}\bodyfont\slshape\color{graytext} #1}}
\newcommand*{\entryemployerstyle}[1]{{\fontsize{11pt}{1em}\bodyfont\bfseries\color{graytext} #1}}
\newcommand*{\entryurlstyle}[1]{{\fontsize{11pt}{1em}\bodyfont\upshape\color{graytext} #1}}
\newcommand*{\entrydescriptionstyle}[1]{{\fontsize{12pt}{1em}\bodyfont\upshape\color{text} #1}}

% {position}{date}{employer}{url}{description}
\renewcommand*{\cventry}[5]{
  \setlength\tabcolsep{0pt}
  \setlength{\extrarowheight}{1ex}
  %\setlength\topsep{-1ex}
  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l r}
    \noalign{\vspace{-2ex}}
    \entrypositionstyle{#1} & \entrydatestyle{#2} \\
    \entryemployerstyle{#3} & \entryurlstyle{\url{#4}} \\
    \multicolumn{2}{L{\textwidth}}{
      \entrydescriptionstyle{#5}
    }
  \end{tabular*}
}

\newenvironment{cvprojects}[1] {%
  \ifthenelse{\equal{#1}{}}{
    \begin{description}[
      itemindent=0em,
      labelwidth=0em,
      labelsep=0em,
      leftmargin=0em,
      parsep=1ex
    ]
  }{
    \begin{description}[
      itemindent=0em,
      labelwidth=0em,
      labelsep=0em,
      leftmargin=0em,
      parsep=1ex,
      topsep=#1
    ]
  }
}{%
  \end{description}
}

% {title}
% {url}
% {short description}
% {technologies}
% {description}
\newcommand{\cvproject}[5]{%
  \ifthenelse{\equal{#1}{}}{}{\textbf{#1}\newline{}\vspace{1ex}}
  \ifthenelse{\equal{#2}{}}{}{\url{#2}\newline{}\vspace{0.8ex}}
  \ifthenelse{\equal{#3}{}}{}{#3\newline{}\vspace{0.8ex}}
  \noindent\emph{Technologies - #4.}\vspace{0.8ex}
  \ifthenelse{\equal{#5}{}}{}{\newline{}#5}
}

\cvsection{Experience}
\begin{cventries}
  \cventry
    {Software developer}
    {Apr 2024 - Present}
    {Molecula.io (remote)}
    {https://molecula.io}
    {
      \cvproject
        {}{}{}
        {Next.js, Cloudflare}
        {
          Led the development of all client-facing applications to support the company's technology, 
          taking end-to-end ownership of frontend systems and infrastructure.
          \hfill \break
          \hfill \break
          Defined and implemented the technology stack: selected Next.js for its scalability and performance, 
          hosted apps on Cloudflare for global delivery, and used Terraform to manage frontend infrastructure independently.
          \hfill \break
          \hfill \break
          Built and launched three key applications:
          - MVP Application: private.molecula.io.\hfill \break
          - Marketing Website and Blog: molecula.io (integrated with Sanity as CMS).\hfill \break
          - Client Beta Application: beta.molecula.io.
          \hfill \break
          \hfill \break
          Collaborated cross-functionally with designers and project managers to finalize UI/UX, 
          establish timelines, and address gaps in requirements with creative problem-solving and independent decision-making.
          \hfill \break
        }
    }
\cventry
    {Software developer}
    {Sep 2022 - Jun 2023}
    {Loóna (remote)}
    {https://loona.app}
    {
      \cvproject
        {}{}{}
        {ReactNative, TypeScript, Objective-C, Java}
        {
          As a member of a mobile engineering team, 
          I actively participated in the implementation of product experiments. 
          Our team had a strong focus on metrics, which drove our fast-paced and 
          highly experimental approach. 
          My responsibilities encompassed the entire project cycle, 
          starting from clarifying ideas with the product team, 
          to executing the implementation, and collaborating with the QA team to 
          ensure stability post-implementation. This routine formed an integral part of my daily work.
          \hfill \break
          \hfill \break
          Some notable contributions I made to the app include:
          - Redesigning the main page, incorporating cards for episodes and other sections.\hfill \break
          - Participating in various aspects of the onboarding process, including past AB tests and non-experimental components.\hfill \break
          - Questionnaries.\hfill \break
          - Collaborating as part of a team on the Dreams AI functionality (which should now be deprecated).\hfill \break
          - Contributing to the Lumos pivot (also likely deprecated) as a team member.
          \hfill \break
        }
    }
\cventry
    {Software developer}
    {Nov 2019 - Aug 2022}
    {EverX (former Tonlabs)}
    {https://everx.dev}
    {
      \begin{cvprojects}{0.8ex}
      \item \cvproject
        {Ever Surf}
        {https://ever.surf}{}
        {ReactNative, TypeScript, Objective-C, Java}
        {
          I worked on developing the Everscale blockchain client, 
          a multi-platform application designed for iOS, Android, and web. 
          The client, often referred to as a wallet in the blockchain industry, 
          offers more than just basic wallet functionality. 
          My primary focus was on improving the user interface and addressing 
          performance-related concerns. With a codebase shared across all platforms, 
          exceeding 90\% similarity, I leveraged my extensive knowledge of React Native 
          internals to overcome any out-of-the-box limitations and successfully resolve related issues.
        }
      \item \cvproject
        {Design system}
        {https://uikit.ever.surf}{}
        {ReactNative, TypeScript, Objective-C, Java}
        {
          I assumed the role of lead developer for the design system, 
          an internal product aimed at providing developers with a set of 
          components that align with our design standards. 
          This system greatly simplifies the process of creating high-quality interfaces, 
          eliminating the need for every developer to possess an in-depth understanding of React Native internals.
          \hfill \break
          \hfill \break
          The design system was used in the app mentioned above, hence all the UI has a touch of my work.
        }
    \end{cvprojects}
    }
\cventry
    {Software developer}
    {Jan 2017 - Nov 2019}
    {EPAM Systems, St. Petersburg, Russia}
    {https://epam.com}
    {
      Multiple projects:\newline
      \begin{cvprojects}{0.8ex}
      \item \cvproject
          {PoC of a mobile application to work with bluetooth devices (tonometrs and pill devices).}
          {}{}
          {ReactNative, JavaScript}
          {Completed the finalization of an existing application for customer presentation.}
      \item \cvproject
          {PoC of a mobile application for medical researches.}
          {}{}
          {ReactNative, JavaScript}
          {Provided ongoing maintenance and support for an existing application, ensuring its readiness for customer presentations.}
      \item \cvproject
          {myPH, miHP}
          {https://itunes.apple.com/ch/app/myph/id1438106777}
          {Mobile applications to monitor client's medications.}
          {ReactNative, TypeScript, Fastlane, Objective-C, Java}
          {
            As the primary individual contributor, 
            I single-handedly managed the end-to-end delivery process, 
            from initial estimations to customer presentations. 
            I engaged in negotiations with customers regarding feature 
            requirements and effectively communicated the development results. 
            Additionally, I took charge of maintaining the CI (Jenkins) system 
            and consistently enhanced our build system.
          }
      \end{cvprojects}
    }
\cventry
    {Frontend software developer}
    {Jul 2016 - Dec 2017}
    {OOO "CNS", Moscow, Russia (remote position)}
    {https://domclick.ru}
    {
      \cvproject
          {Mortgage service}
          {}
          {The main idea behind the project was to reduce offline effort for a client to get a mortgage.}
          {JavaScript (React, Redux), Docker}
          {
            I was primarily responsible for the frontend development 
            of \href{http://ipoteka.domclick.ru}{ipoteka.domclick.ru} 
            as part of an agile team. Throughout the project, 
            I managed the entire development cycle, from initial estimations 
            to final delivery. One of my notable accomplishments was achieving 
            frequent releases, with a cadence of almost daily updates at 
            certain stages and typically multiple times per week. 
            Ensuring the quality of my work was a top priority, and I worked 
            closely with QA engineers to achieve this goal.
            \hfill \break
          }
    }
\cventry
    {Frontend software developer}
    {Jun 2015 - Jun 2016}
    {Calvera, St. Petersburg, Russia}
    {http://calvera.su}
    {
      Multiple projects:\newline
      \begin{cvprojects}{0.8ex}
        \item \cvproject
            {Real estate search service}
            {}
            {The service was built around an idea of a detailed view of real estates with detailed description, lots of photos and blueprints.}
            {JavaScript (backbone, marionette, virtual-dom)}
            {
              I played a pivotal role in developing a critical component 
              of the project, specifically the detailed view of a real estate 
              object. As the primary frontend developer for this page, I was 
              responsible for creating nearly all of its functionality. 
              Throughout the project's lifecycle, I collaborated with junior developers, 
              providing guidance and support as needed. 
              Additionally, I took charge of setting up the team's development environment, 
              including the establishment of a robust build system and other necessary components.
            }
        \item \cvproject
            {Book reader}
            {}
            {Our investor had a book and wanted to have a mobile application for it.}
            {ReactNative, ClojureScript}
            {I successfully developed a comprehensive application specifically designed for iPad devices.}
      \end{cvprojects}
    }
\cventry
    {Junior software developer}
    {Jan 2014 - April 2014}
    {ICreative, Omsk, Russia}{}
    {
      Multiple projects\newline
      \vspace{0.8ex}
      \cvproject
          {}{}{}
          {JavaScript, PHP}
          {
            I was part of a small outsourced team, 
            where I contributed to both maintaining 
            existing projects and developing new ones. 
            I actively assisted senior colleagues in their tasks 
            and also took the opportunity to learn and work with 
            JavaScript (JS) and PHP. While working under the supervision 
            of the team lead, I made efforts to independently solve 
            assigned tasks, gaining valuable experience along the way.
          }
    }
\end{cventries}

\cvsection{Education}
\cvsubsection{University}
\begin{cventries}
\cventry
    {Irkutsk State University of Railway Transportation}
    {Sep 2009 - Jun 2014}
    {Engineer}
    {}
    {}
\end{cventries}

\end{document}
